SKIN LESION CLASSIFICATION ON IMBALANCED DATA USING DEEP LEARNING WITH SOFT ATTENTION

### 2022-09-03 MDPI/Sensor Paper/template.tex
Update

\address{
$^{1}$ \quad School of Electrical and Electronic Engineering, Hanoi university of Science and Technology, Vietnam; dung.nguyenviet1@hust.edu.vn\\
$^{2}$ \quad Faculty of Information Technology, University of Transport and Communications, Vietnam; dnbui@utc.edu.vn\\
$^{3}$ \quad School of Electrical and Electronic Engineering, Hanoi university of Science and Technology, Vietnam; khoi.dh200322@sis.hust.edu.vn}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
\subsection{Experimental Setup}
\subsubsection{Training}
Before training, the data set is split into two sub set for training (90 percent) and validation (10 percent). Test set, otherwise is provided by the HAM10000 data set, contains 857 images. To analyze the effect of augmented data on the model, during the training the image data is augmented by the following technique:\\
- Rotation Range: rotate the image in a fixed angle. \\
- Width and height shift range: Shift the image horizontally and vertically, respectively. \\
- Zoom Range:  Zoom in or zoom out the image to create new image. \\
- Horizontal and vertical flipping: Flipping the image horizontally and vertically to create new image.\\
Otherwise, all of models is trained with the Adam Optimizer \cite{6980} with the learning rate of $0.001$ which is reduced by a factor of $0.2$ to a minimum learning rate of $0.1 x 10^6$, and the epsilon is set to $0.1$. The initial epochs is set to 250 epochs and the Early Stopping is also applied to stop the training as the accuracy of validation set does not increase after $25$ epochs. Besides, the batch size is set to $32$.

@@

\begin{table}[H]
	\centering
	\begin{tabular}{| l | c  c | }
		\hline
		Model & ACC(AD) & ACC(MD)\\ 
		\hline
		InceptionResNetV2 & 0.79 & \textbf{0.90}\\
		\hline
		DenseNet201 & 0.84 & \textbf{0.89}\\
		\hline
		ResNet50 & 0.76 & 0.70 \\
		\hline
		ResNet152 & - & 0.57\\
		\hline
		NasNetLarge & - & 0.84\\
		\hline
		MobileNetV2 & - & 0.81\\
		\hline
		MobileNetV3Small & - & 0.78\\
		\hline
		MobileNetV3Large & - & \textbf{0.86}\\
		\hline
		NasNetMobile & - & \textbf{0.86}\\
		\hline
	\end{tabular}
	\caption{Accuracy of all models. ACC stands for accuracy. AD stands for augmented data, this indicate that the model is trained with augmented data. MD stands for Metadata which indicate that the model is trained with Metadata}
	\label{table:overall-acc}
\end{table}

>>>>

\address{
$^{1}$ \quad School of Electrical and Electronic Engineering, Hanoi University of Science and Technology, Vietnam; dung.nguyenviet1@hust.edu.vn\\
$^{2}$ \quad Faculty of Information Technology, University of Transport and Communications, Vietnam; dnbui@utc.edu.vn\\
$^{3}$ \quad School of Electrical and Electronic Engineering, Hanoi University of Science and Technology, Vietnam; khoi.dh200322@sis.hust.edu.vn}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
\subsection{Experimental Setup}
\subsubsection{Training}
Before training, the data set is split into two sub set for training (90 percent) and validation (10 percent). Test set, otherwise is provided by the HAM10000 data set, contains 857 images. To analyze the effect of augmented data on the model, before the training the image data is augmented to 53573 images by the following technique:\\
- Rotation Range: rotate the image in a fixed angle. \\
- Width and height shift range: Shift the image horizontally and vertically, respectively. \\
- Zoom Range:  Zoom in or zoom out the image to create new image. \\
- Horizontal and vertical flipping: Flipping the image horizontally and vertically to create new image.\\
Otherwise, all of models is trained with the Adam Optimizer \cite{6980} with the learning rate of $0.001$ which is reduced by a factor of $0.2$ to a minimum learning rate of $0.1 x 10^6$, and the epsilon is set to $0.1$. The initial epochs is set to 250 epochs and the Early Stopping is also applied to stop the training as the accuracy of validation set does not increase after $25$ epochs. Besides, the batch size is set to $32$.

@@

\begin{table}[H]
	\centering
	\begin{tabular}{| l | c  c | }
		\hline
		Model & ACC(AD) & ACC(MD)\\ 
		\hline
		InceptionResNetV2 & 0.79 & \textbf{0.90}\\
		\hline
		DenseNet201 & 0.84 & \textbf{0.89}\\
		\hline
		ResNet50 & 0.76 & 0.70\\
		\hline
		ResNet152 & 0.81 & 0.57\\
		\hline
		NasNetLarge & - & 0.84\\
		\hline
		MobileNetV2 & - & 0.81\\
		\hline
		MobileNetV3Small & - & 0.78\\
		\hline
		MobileNetV3Large & 0.85 & \textbf{0.86}\\
		\hline
		NasNetMobile & 0.84 & \textbf{0.86}\\
		\hline
	\end{tabular}
	\caption{Accuracy of all models. ACC stands for accuracy. AD stands for augmented data, this indicate that the model is trained with augmented data. MD stands for Metadata which indicate that the model is trained with Metadata}
	\label{table:overall-acc}
\end{table}
